Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-06-04 paper.qmd
Update

In conclusion, while our method effectively captures and represents high-dimensional data structures, further enhancements could involve introducing approaches to bind the data and indicate line segments beyond \gD{}. These improvements would help in creating a more accurate representation of the data when \gD{} layout is inadequate.

>>>>

In conclusion, while our method effectively captures and represents high-dimensional data structures, further enhancements could involve introducing approaches to bind the data, indicate line segments beyond \gD{}, and diagnose the fitted model. These improvements would help in creating a more accurate representation of the data when \gD{} layout is inadequate.
